MSDS6371Project

### 2020-11-21 MSDS6371Project.Rmd
update with stepwise output

### Stepwise Selection
```{r}
set.seed(11)
train.control <- trainControl(method = "cv", number = 10)
step.model = train(lSalePrice~.-Id, data=variables.used,
                   method="lmStepAIC",
                   trControl = train.control,
                   trace=FALSE)
step.model$results
step.model$finalModel
summary(step.model$finalModel)
```

>>>>

### Stepwise Selection
```{r}
set.seed(11)
train.control <- trainControl(method = "cv", number = 10)
step.model = train(lSalePrice~.-Id, data=variables.used,
                   method="lmStepAIC",
                   trControl = train.control,
                   trace=FALSE)
step.model$results
step.model$finalModel
summary(step.model$finalModel)
print(step.model)
exp(0.1494448)
```

### Load in Test Data 
```{r}
#Load in test.csv
testData = read.csv("/Users/mingyang/Desktop/SMU/StatisticalFoundation_Fall2020/MSDS6371Project/test.csv",header = TRUE)
#Convert variables we need from N/A to NONE
testData$MasVnrArea = ifelse(is.na(testData$MasVnrArea),0,testData$MasVnrArea)
testData$TotalBsmtSF = ifelse(is.na(testData$TotalBsmtSF),0,testData$TotalBsmtSF)
testData$GarageCars = ifelse(is.na(testData$GarageCars),0,testData$GarageCars)
testData$MSZoning = ifelse(is.na(testData$MSZoning),"RL",testData$MSZoning)
testData$KitchenQual = ifelse(is.na(testData$KitchenQual),"TA",testData$KitchenQual)
testData$MSSubClass = ifelse(testData$MSSubClass==150,180,testData$MSSubClass)
testData$FullBath = ifelse(testData$FullBath==4,3,testData$FullBath)
testData$Fireplaces = ifelse(testData$Fireplaces==4,3,testData$Fireplaces)

testData$BsmtQual = ifelse(is.na(testData$BsmtQual),"NONE",testData$BsmtQual)
testData$BsmtCond = ifelse(is.na(testData$BsmtCond),"NONE",testData$BsmtCond)
testData$GarageType = ifelse(is.na(testData$GarageType),"NONE",testData$GarageType)
#Convert some variables we need into factor
testData[cols.to.factor] = lapply(testData[cols.to.factor],factor)
#create variable PoolYN
testData$PoolYN = ifelse(is.na(testData$PoolQC),"NO","YES")
testData$PoolYN = as.factor(testData$PoolYN)
#select variables needed for testing
testVariable = testData %>% 
  dplyr::select(Id,MSSubClass,MSZoning,LotArea,LotConfig,Neighborhood,HouseStyle,
         OverallQual,OverallCond,YearBuilt,YearRemodAdd,MasVnrArea,ExterQual,
         ExterCond,Foundation,BsmtQual,BsmtCond,TotalBsmtSF,
         Heating,CentralAir,X1stFlrSF,GrLivArea,FullBath,KitchenQual,TotRmsAbvGrd,
         Fireplaces,GarageType,GarageCars,PoolYN,MoSold,YrSold)

### run stepwise test and export result to csv file - Kaggle Score 0.15372
```{r}
testVariable$lSalePrice = predict(step.model,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePrice)
result.stepwise = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.stepwise,"stepwise_Prediction_Miller_YU.csv",row.names = FALSE)
```
